УДК 911.3

### 2025-02-05 legal-companies-migration/journal-article/Paper.Rmd
Reorganise files and adjust code for two papers about legal companies migration, #6

---
title: "УДК 911.3"
subtitle: "Релокация юридических компаний в России в 2016–2023 гг."
author: Сёмин П. О.
output: 
  word_document:
    reference_docx: reference.docx
bibliography: biblio-ru.bib
csl: "biblio-styles-ru.csl"

@@

```{r imports, include=FALSE, cache=TRUE}
source("Script.R")
```

>>>>

---
title: "УДК 911.3"
subtitle: "Релокация юридических компаний в России в 2016–2023 гг."
author: Сёмин П. О.
output: 
  word_document:
    reference_docx: assets/reference.docx
bibliography: assets/biblio-ru.bib
csl: assets/biblio-styles-ru.csl

@@

```{r imports, include=FALSE, cache=TRUE}
source("helpers/Script.R")
```
